\textbf{Appendix}\\ Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-08-21 Chapter_0/04_Manuscript/Manuscript_Backup_2020-04-27.tex
first commit

\documentclass[abstract=on,10pt,a4paper,bibliography=totocnumbered]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{epstopdf}
\usepackage[onehalfspacing]{setspace}
\usepackage[paper=a4paper,left=30mm,right=30mm,top=20mm,bottom=25mm]{geometry}
\usepackage[round]{natbib}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[labelfont=bf]{caption}
\usepackage{footnote}
\usepackage{tabularx}
\usepackage{gensymb}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{varwidth}
% \usepackage[nomarkers,figuresonly]{endfloat}
\usepackage{csvsimple}
\usepackage{arydshln}
\usepackage{titlesec}

@@

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
        \node[anchor=south west,inner sep=0] (image) at (0,0,0) {
        \includegraphics[width=0.9\textwidth]{99_StudyArea2.pdf}
        };
        \begin{scope}[x={(image.south east)},y={(image.north west)}]
            % % next four lines will help you to locate the point needed by forming a grid.
            % % comment these four lines in the final picture.
            % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
            % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
            % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
            % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
            % % upto here
            \draw[black] (0.202, 0.255) -- (0.36, 0.955);
            \draw[black] (0.202, 0.205) -- (0.36, 0.070);
        \end{scope}
    \end{tikzpicture}
    \caption{Overview of our study area. (a) The red rectangle depicts our
    \textit{extended study area}, which was confined by the extent of the
    KAZA-TFCA. Purple areas indicate remaining wild dog populations according to
    the IUCN \citep{Woodroffe.2012}. (b) The orange rectangle illustrates our
    \textit{core study area}, from which all dispersers departed. Yellow lines
    depict all dispersal trajectories that were recorded between the years 2011
    and 2019. Since game reserves in Botswana virtually serve the same purpose as
    National Parks, we will use the terms interchangeably for this region.}
    \label{StudyArea}
  \end{center}
\end{figure}

@@

% Some Summary Statistics
In total, we collected 4'691 GPS relocations during dispersal (see
\Cref{Trajectories}). In our analysis, we did not differentiate between male and
female dispersing coalitions, for previous research found little differences
between sexes during dispersal (\citeauthor{Woodroffe.2019}, 2019;
\citeauthor{Cozzi.2020}, unpublished). On average, dispersal coalitions included
three individuals (min = 1, max = 7), dispersed for 41 days (min = 7, max =
133), and covered a mean cumulative distance of 370 km (min = 105, max = 610).

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = \textwidth]{99_Trajectories2.pdf}
    \caption{Illustration of the dispersal trajectories that we recorded. Each
    color represents a different dispersal coalition. All coalitions departed
    from the core study area, which is indicated by the white rectangle. The
    coalition dispersing towards the far east of the map covered over 360 km in
    under 10 days.}
    \label{Trajectories}
  \end{center}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = \textwidth]{99_Covariates.pdf}
    \caption{Overview of covariates that we used in our models. Although all
    covariates were prepared for the extended study area, we present only an
    extract to maximize visibility. The white rectangle in each plot depicts our
    core study area. (a) Averaged layer of all binary maps of water and dryland
    that we acquired using our floodmapping algorithm. (b) Percentage cover of
    trees. (c) Percentage cover of shrubs/grassland. Note that anything not
    covered by trees or shrubs/grassland was deemed to be bare land. (d)
    Protection status of the area. (e) Human influence proxy, taking into
    account human density, farms, and roads. (f) Distance to nearest road (white
    lines depict actual roads).}
    \label{Covariates}
  \end{center}
\end{figure}

@@

We extracted spatial covariates along realized and random steps as listed in
\Cref{ExtractedCovars}. For continuous covariates, we calculated the average
value, for binary covariates the percentage cover along the step. Since our
floodmaps were dynamic, we extracted values from the floodmap that was closest
in date to the actual step. We further derived a binary variable indicating
whether or not a step crossed a road and we identified the average distance of
each step to the nearest source of water or the nearest road. We square-rooted
the values for \textit{DistanceToRoads} and \textit{DistanceToWater} to render a
decreasing marginal impact of distance. We standardized extracted covariates to
a mean of zero and a standard deviation of one using a z-score transformation.
Furthermore, we screened covariates for correlation using Pearson's Correlation
Coefficient. None of the covariates were overly correlated (\(|r| > 0.6\),
\citealp{Latham.2011}) and we retained all of them for modeling. To run a proper
iSSF analysis, we also included two movement metrics, namely the cosine of the
turning angle (\(cos(ta)\)) and the logarithm of the step length (\(log(sl)\)),
as covariates in our models \citep{Avgar.2016}. The movement metric \(cos(ta\))
served to describe the directionality of a step, as it transformed the circular
measure of (\(-\pi, +\pi\)) into a linear measure (-1, 1). Thus, positive values
indicated forward movements, whereas negative values indicated backward
movements \citep{Turchin.1998}. The movement metric \(log(sl\)), on the other
hand, was included as an indicator of the preferred step length. Since steps
were regularly spaced by four hours, \(log(sl\)) can also be interpreted as
movement rate.

\begin{table}[h]
  \begin{center}
    \caption{Overview of spatial covariates extracted along steps (see
    \Cref{Sources} in \Cref{Appendix:Sources} for an overview of the sources and
    resampling methods). *The covariates \textit{Water} and \textit{Dryland}
    added up to 100\%, which is why only \textit{Water} was included as
    explanatory variable in our models. The same applied for the group
    \textit{Shrubs/Grassland}, \textit{Trees}, and \textit{Bareland}, where we
    omitted \textit{Bareland} for modeling. Finally, from the group
    \textit{Protected} and \textit{Pastoral}, we only included
    \textit{Protected} in our models.}
    \label{ExtractedCovars}
    \resizebox{\textwidth}{!} {
      \begin{tabular}{lllll}
      \hline
      \textbf{Category} &
        \textbf{Covariate} &
          \textbf{Description} &
            \textbf{Values} \\
              % \textbf{Source(s)} \\
      \midrule
      \multirow{5}{*}{Land Cover}
        & Water
          & Percentage cover of water along step
            & 0-100\%\\
              % & \cite{Chen.2015}, \cite{Schaaf.2015}, \cite{Yamazaki.2019} \\
        & Dryland*
          & Percentage cover of dryland along step
            & 0-100\%\\
              % & Globeland, \cite{Schaaf.2015}, \cite{Yamazaki.2019} \\
        & DistanceToWater
          & Average distance of step to nearest water source
            & \(\geq\) 0m\\
              % & Globeland, \cite{Schaaf.2015}, \cite{Yamazaki.2019} \\
        & Shrubs/Grassland
          & Average non-tree vegetation along step
            & 0-100\%\\
              % & \cite{Dimiceli.2015} \\
        & Trees
          & Average tree-vegetation along step
            & 0-100\%\\
              % & \cite{Dimiceli.2015} \\
        & Bareland*
          & Average non-vegetated area along step
            & 0-100\%\\
              % & \cite{Dimiceli.2015} \\
      \hdashline
      \multirow{2}{*}{Protection Status}
        & Protected
          & Percentage cover of protected area along step
            & 0-100\%\\
              % & \cite{PeaceParks.2019} \\
        & Pastoral*
          & Percentage cover of unprotected area along step
            & 0-100\%\\
              % & \cite{PeaceParks.2019} \\
      \hdashline
      \multirow{3}{*}{Human Influence}
        & HumansBuffer5000
          & Average buffered (5 km) human influence along step
            & \(\geq\) 0\\
              % & \cite{Facebook.2019}, \cite{OpenStreetMap.2019}, \cite{Chen.2015}, \cite{Xiong.2017}\\
        & DistanceToRoads
          & Average distance of step to nearest road
            & \(\geq\) 0m\\
              % & \cite{Facebook.2019}, \cite{OpenStreetMap.2019}, \cite{Chen.2015}, \cite{Xiong.2017}\\
        & RoadCrossing
          & Binary value indicating whether a step crossed a road
            & 0, 1\\
              % & \cite{Facebook.2019}, \cite{OpenStreetMap.2019}, \cite{Chen.2015}, \cite{Xiong.2017}\\
      \hline
      \end{tabular}
    }
  \end{center}
\end{table}

@@

% \begin{figure}[hbtp]
%   \begin{center}
%     \begin{tikzpicture}
%         \node[anchor=south west,inner sep=0] (image) at (0,0,0) {
%           \begin{minipage}{0.54\textwidth}
%             \begin{center}
%               \includegraphics[width = 0.5\textwidth]
%                 {99_LeastCostPaths(Example1).pdf}\\
%               \includegraphics[width = 1.0\textwidth]
%                 {99_LeastCostPaths(Example2).pdf}\\
%             \end{center}
%           \end{minipage}
%         };
%         \begin{scope}[x={(image.south east)},y={(image.north west)}]
%            %  % next four lines will help you to locate the point needed by
%            %  % forming a grid. comment these four lines in the final picture.↓
%            % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
%            % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
%            % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
%            % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
%            %  % upto here
%             % \draw[black, line width = 0.5pt] (0.389, 0.627) -- (0.080, 0.477);
%             % \draw[black, line width = 0.5pt] (0.582, 0.627) -- (0.980, 0.477);
%             % \draw[white, line width = 1pt] (0.675, 0.290) -- (0.720, 0.265);
%             % \draw[white, line width = 1pt] (0.840, 0.255) -- (0.800, 0.260);
%             % \draw[white, line width = 1pt] (0.807, 0.205) -- (0.752, 0.205);
%         \end{scope}
%     \end{tikzpicture}
%     \caption{Figures illustrating the process of identifying a least-cost
%     corridor between the source points A and B. (a) Example of a permeability
%     surface, which serves to determine the costs of movement. (b1) Cumulative
%     cost map for point A, depicting the total minimal costs necessary to get
%     from point A to every other location. (b2) Cumulative cost map for point B,
%     depicting the total minimal costs necessary to get from point B to every
%     other location. (c) Summed cost maps of points A and B. (d) Masked out
%     corridor containing pixels that do not exceed the cheapest pixel by more
%     than 5\%.}
%     \label{LCCExample}
%   \end{center}
% \end{figure}

\begin{figure}[hbtp]
  \begin{center}
  \begin{minipage}{.25\linewidth}
    \begin{subfigure}[t]{.9\linewidth}
        \includegraphics[width=\textwidth]{99_LeastCostPaths(Example1).pdf}
    \end{subfigure}
  \end{minipage}
  \begin{minipage}{.25\linewidth}
    \begin{subfigure}[t]{.9\linewidth}
        \includegraphics[width=\textwidth]{99_LeastCostPaths(Example2).pdf}
    \end{subfigure}
  \end{minipage}
  \begin{minipage}{.25\linewidth}
    \begin{subfigure}[t]{.9\linewidth}
        \includegraphics[width=\textwidth]{99_LeastCostPaths(Example3).pdf}
    \end{subfigure}
  \end{minipage}
  \caption{Figures illustrating the process of identifying a least-cost corridor
  between source points A and B following \cite{Pinto.2009}. (a) Example of a
  permeability surface, which determines the costs of movement. (b1) Cumulative
  cost map for point A, depicting the total minimal costs necessary to get from
  point A to every other location. (b2) Cumulative cost map for point B,
  depicting the total minimal costs to get from point B to every other location.
  (c) Summed cost maps of points A and B. (d) Masked out corridor containing
  pixels that do not exceed the cheapest pixel by more than 5\%.}
  \label{LCCExample}
  \end{center}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = \textwidth]{99_PermeabilityResults.pdf}
    \caption{(a) Estimated selection coefficients from the most parsimonious
    habitat selection model. Negative coefficients indicate avoidance of a
    covariate, positive coefficients selection of a covariate. Whiskers
    delineate the 95\%-CIs for estimated parameters. The intercept is
    meaningless in the iSSF framework and was thus omitted. (b) Results from the
    k-fold cross validation for case-control studies. The left graph shows rank
    frequencies of \textit{realized} steps according to predictions, whereas the
    right graph shows rank frequencies of \textit{randomly selected} steps
    according to predictions. \(\bar{r}_s\) indicates the mean correlation
    coefficient resulting from 100 repetitions of the k-fold cross validation.
    The blue smoothing line was fitted using a LOESS regression and solely
    serves to aid the eye in detecting the trends. Correlation coefficients
    suggest that our prediction is significant and robust, evidenced by the fact
    that the confidence intervals of \(\bar{r}_{s, realized}\) and \(\bar{r}_{s,
    random}\) do not overlap and that there is strong and significant
    correlation between ranks and associated frequency for realized steps.}
    \label{PermeabilityResults}
  \end{center}
\end{figure}

@@

% \newgeometry{left=30mm,right=30mm,top=0mm,bottom=20mm}
% \begin{figure}[hbtp]
%   \begin{center}
%     \begin{tikzpicture}
%         \node[anchor=south west,inner sep=0] (image) at (0,0,0) {
%           \begin{minipage}{0.95\textwidth}
%             \includegraphics[width = \textwidth]{99_PermeabilityMap.pdf}
%             \includegraphics[width = \textwidth]{99_PermeabilityMap2.pdf}
%           \end{minipage}
%         };
%         \begin{scope}[x={(image.south east)},y={(image.north west)}]
%            %  % next four lines will help you to locate the point needed by
%            %  % forming a grid. comment these four lines in the final picture.↓
%            % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
%            % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
%            % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
%            % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
%            %  % upto here
%             \draw[black, line width = 1pt] (0.389, 0.627) -- (0.080, 0.477);
%             \draw[black, line width = 1pt] (0.582, 0.627) -- (0.980, 0.477);
%             \draw[white, line width = 1pt] (0.675, 0.290) -- (0.720, 0.265);
%             \draw[white, line width = 1pt] (0.840, 0.255) -- (0.800, 0.260);
%             \draw[white, line width = 1pt] (0.807, 0.205) -- (0.752, 0.205);
%         \end{scope}
%     \end{tikzpicture}
%     \caption{(a) Predicted permeability surface for the extent of the KAZA-TFCA.
%     Permability was predicted by calculating selection scores \(w(x)\) for each
%     pixel based on the pixel's underlying covariates. Areas that dispersers find
%     easy to traverse are depicted in bright colors. Bold white lines delineate
%     the borders of the KAZA-TFCA, whereas dashed white lines show country
%     borders. (b) Detailed view of the Okavango Delta and Linyanti Swamp region,
%     which appears to provide the most suitable landscape for dispersers. The
%     white square highlights the core study area.}
%     \label{PermeabilityMap}
%   \end{center}
% \end{figure}
% \restoregeometry

% \newgeometry{left=30mm,right=30mm,top=0mm,bottom=20mm}
\begin{figure}[hbtp]
  \begin{center}
    \begin{tikzpicture}
        \node[anchor=south west,inner sep=0] (image) at (0,0,0) {
          \begin{minipage}{0.65\textwidth}
            \includegraphics[width = \textwidth]{99_PermeabilityMap.pdf}
          \end{minipage}
        };
        \begin{scope}[x={(image.south east)},y={(image.north west)}]
           %  % next four lines will help you to locate the point needed by
           %  % forming a grid. comment these four lines in the final picture.↓
           % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
           % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
           % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
           % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
           %  % upto here
          % \node[text=white, circle, scale=1, font=\bfseries, inner sep = 0.5pt
          %   , draw=white] (No1) at (0.440, 0.350){1};
          % \node[text=white, circle, scale=1, font=\bfseries, inner sep = 0.5pt
          %   , draw=white] (No2) at (0.520, 0.438){2};
        \end{scope}
    \end{tikzpicture}
    \caption{Predicted permeability surface for the extent of the KAZA-TFCA.
    Permability was predicted by calculating selection scores \(w(x) =
    exp(\beta_1 x_1 + \beta_2 x_2 + ... + \beta_n x_n)\) for each pixel based on
    the pixel's underlying covariates (\(x_i\)) and estimated habitat
    preferences (\(\beta_i\)). Areas that dispersers find easy to traverse are
    depicted in bright colors. Bold white lines delineate the borders of the
    KAZA-TFCA, whereas dashed white lines show country borders.}
    \label{PermeabilityMap}
  \end{center}
\end{figure}
% \restoregeometry

% \begin{table}[h]
%   \caption{Comparison of median permeability across countries, separated
%   according to areas within and outside the KAZA-TFCA, as well as within and
%   outside protected areas. High values indicate high permeability, whereas low
%   values correspond to low permeability.}
%   \label{PermeabilityComp}
%   \begin{center}
%     \resizebox{\textwidth}{!} {
%       \begin{tabular}{llllllllr}
%       & & \multicolumn{2}{c}{KAZA-TFCA} && \multicolumn{2}{c}{Protection Status} \\
%       \cline{3-4} \cline{6-7}
%       Country & & Inside & Outside & & Protected & Pastoral & & Overall \\
%       \hline
%       Angola & & 1.67 & 0.59 & & 1.67 & 0.60 & & 1.03 \\
%       Namibia & & 0.91 & 0.49 & & 0.98 & 0.44 & & 0.59 \\
%       Botswana & & 1.17 & 0.69 & & 1.37 & 0.62 & & 0.91 \\
%       Zimbabwe & & 0.25 & 0.18 & & 0.32 & 0.17 & & 0.19 \\
%       Zambia & & 0.26 & 0.12 & & 0.23 & 0.13 & & 0.15 \\
%       \hline
%       Overall & & 0.75 & 0.26 & & 0.74 & 0.27 & & 0.38 \\
%       \end{tabular}
%     }
%   \end{center}
% \end{table}

\begin{table}[h]
  \caption{Comparison of median permeability (interquantile range in brackets)
  across countries, separated according to areas within and outside the
  KAZA-TFCA, as well as within and outside formally protected areas. High values
  indicate high permeability, whereas low values correspond to low
  permeability.}
  \label{PermeabilityComp}
  \begin{center}
    \resizebox{0.9\textwidth}{!} {
      \begin{tabular}{llllllllr}
      & & \multicolumn{2}{c}{KAZA-TFCA} && \multicolumn{2}{c}{Protection Status} \\
      \cline{3-4} \cline{6-7}
      Country & & Inside & Outside & & Protected & Pastoral & & Overall \\
      \hline
      Angola & & 0.46 (0.42) & 0.18 (0.40) & & 0.46 (0.42) & 0.18 (0.40) & & 0.29 (0.45) \\
      Namibia & & 0.26 (0.39) & 0.13 (0.20) & & 0.27 (0.38) & 0.12 (0.16) & & 0.16 (0.31) \\
      Botswana & & 0.33 (0.38) & 0.19 (0.23) & & 0.38 (0.35) & 0.17 (0.23) & & 0.25 (0.33) \\
      Zimbabwe & & 0.06 (0.25) & 0.05 (0.04) & & 0.09 (0.26) & 0.04 (0.03) & & 0.05 (0.07) \\
      Zambia & & 0.07 (0.11) & 0.03 (0.05) & & 0.06 (0.11) & 0.03 (0.05) & & 0.04 (0.07) \\
      \hline
      Overall & & 0.21 (0.39) & 0.07 (0.18) & & 0.21 (0.39) & 0.07 (0.18) & & 0.11 (0.29) \\
      \end{tabular}
    }
  \end{center}
\end{table}

@@

\newpage
\appendix
\section{Appendix}
\subsection{Floodmapping Algorithm}
\label{Appendix:FloodmappingAlgorithm}
To implement the floodmapping algorithm, we defined two sets of polygons located
in the region of the Okavango Delta (see \Cref{Floodmapping}). The first set
consisted of areas known to be permanent dryland, whereas the second set
consisted of permanent waters. Since we were unable to retrieve the original
polygons used in \cite{Wolski.2017}, we geo-referenced one of their
illustrations and traced the polygons there. After recreation of the polygons,
we used the R-package \textit{getSpatialData} \citep{Schwalb.2018} to download
and pre-process all relatively cloud-free MODIS Terra images (MCD43A4,
\citealp{Schaaf.2015}) available for the period of our dispersal events.
Assessment of cloud cover was based on visual inspection of MODIS images on
ORI's website \citep{ORI.2019}. The MCD43A4 MODIS product is particularly useful
for dynamic floodmapping because it is updated with new composite images every
8\textsuperscript{th} day \citep{Wolski.2017}. After download, we classified
each MODIS image into a binary map of water (flood) and dryland using a
threshold that was identified as follows. First, we extracted all reflectance
values of MODIS Terra Band 7 within the water- and dryland-polygons. Second, we
computed histograms of water-reflectances and dryland-reflectances and
empirically verified that reflectances of the two groups were sufficiently
distinct. More specifically, we checked if superimposing the two histograms
resulted in a bimodal plot. This was said to be achieved if the
99\textsuperscript{th} percentile of water-reflectances did not severely exceed
the 1\textsuperscript{st} percentile of dryland-reflectances (\(p_{0.99, water}
- \frac{10}{255} < p_{0.01, dryland}\)). Third, if peaks were sufficiently
different, we calculated a threshold (\(t\)) using \Cref{EQ1}:

>>>>

\documentclass[abstract=on,10pt,a4paper,bibliography=totocnumbered]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{epstopdf}
\usepackage[onehalfspacing]{setspace}
\usepackage[paper=a4paper,left=30mm,right=30mm,top=20mm,bottom=25mm]{geometry}
\usepackage[round]{natbib}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[labelfont=bf]{caption}
\usepackage{footnote}
\usepackage{tabularx}
\usepackage{gensymb}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{varwidth}
\usepackage{csvsimple}
\usepackage{arydshln}
\usepackage{titlesec}
\usepackage{float}

@@

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
        \node[anchor=south west,inner sep=0] (image) at (0,0,0) {
        \includegraphics[width=0.9\textwidth]{99_StudyArea.pdf}
        };
        \begin{scope}[x={(image.south east)},y={(image.north west)}]
            % % next four lines will help you to locate the point needed by forming a grid.
            % % comment these four lines in the final picture.
            % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
            % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
            % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
            % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
            % % upto here
            \draw[black] (0.202, 0.255) -- (0.36, 0.955);
            \draw[black] (0.202, 0.205) -- (0.36, 0.070);
        \end{scope}
    \end{tikzpicture}
    \caption{Overview of our study area. (a) The red rectangle depicts the study
    area, which was confined by a bounding box encompassing the entire
    KAZA-TFCA. Pink areas indicate remaining wild dog populations according to
    the IUCN \citep{Woodroffe.2012}. (b) The white rectangle illustrates the
    area within which dispersal coalitions were collared. Since game reserves in
    Botswana virtually serve the same purpose as National Parks, we use the
    terms interchangeably for this region.}
    \label{StudyArea}
  \end{center}
\end{figure}

@@

% Some Summary Statistics
In total, we collected 4'691 GPS relocations during dispersal (see
\Cref{Trajectories} in \Cref{Appendix:GPSData}). In our analysis, we did not
differentiate between male and female dispersing coalitions, for previous
research found little differences between sexes during dispersal
(\citeauthor{Woodroffe.2019}, 2019; \citeauthor{Cozzi.2020}, unpublished). On
average, dispersal coalitions included three individuals (min = 1, max = 7),
dispersed for 41 days (min = 7, max = 133), and covered a mean cumulative
distance of 370 km (min = 105, max = 610).

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = \textwidth]{99_Covariates.pdf}
    \caption{Overview of spatial covariates that we included in our models. We
    prepared all covariates for the entire study area but for better visibility
    we only plot them for the surroundings of the Okavango Delta. The white
    rectangle in each plot depicts the area within which dispersal coalitions
    were collared. (a) Averaged layer of all dynamic (binary) watermaps. (b)
    Percentage cover of trees. (c) Percentage cover of shrubs/grassland.
    Anything that was not covered by trees or shrubs/grassland was deemed to be
    bare land. (d) Protection status of the area. (e) Human influence proxy
    composed of human density, farms, and roads. (f) Distance to nearest road
    (white lines depict actual roads).}
    \label{Covariates}
  \end{center}
\end{figure}

@@

We extracted spatial covariates along realized and random steps as listed in
\Cref{Appendix:Sources}. For continuous covariates, we calculated the average
value, for binary covariates the percentage cover along the step. Since our
floodmaps were dynamic, we extracted values from the floodmap that was closest
in date to the actual step. We further derived a binary variable indicating
whether or not a step crossed a road and we identified the average distance of
each step to the nearest source of water or the nearest road. We square-rooted
the values for \textit{DistanceToRoads} and \textit{DistanceToWater} to render a
decreasing marginal impact of distance. We standardized extracted covariates to
a mean of zero and a standard deviation of one using a z-score transformation.
Furthermore, we screened covariates for correlation using Pearson's Correlation
Coefficient. None of the covariates were overly correlated (\(|r| > 0.6\),
\citealp{Latham.2011}) and we retained all of them for modeling. To run a proper
iSSF analysis, we also included two movement metrics, namely the cosine of the
turning angle (\(cos(ta)\)) and the logarithm of the step length (\(log(sl)\)),
as covariates in our models \citep{Avgar.2016}. The movement metric \(cos(ta\))
served to describe the directionality of a step, as it transformed the circular
measure of (\(-\pi, +\pi\)) into a linear measure (-1, 1). Thus, positive values
indicated forward movements, whereas negative values indicated backward
movements \citep{Turchin.1998}. The movement metric \(log(sl\)), on the other
hand, was included as an indicator of the preferred step length. Since steps
were regularly spaced by four hours, \(log(sl\)) can also be interpreted as
movement rate.

@@

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = \textwidth]{99_PermeabilityResults.pdf}
    \caption{(a) Estimated selection coefficients from the most parsimonious
    habitat selection model. Negative coefficients indicate avoidance of a
    covariate, positive coefficients selection of a covariate. Whiskers
    delineate the 95\%-CIs for estimated parameters. (b) Results from the k-fold
    cross validation for case-control studies. The left graph shows rank
    frequencies of \textit{realized} steps according to predictions, whereas the
    right graph shows rank frequencies of \textit{randomly selected} steps
    according to predictions. \(\bar{r}_s\) indicates the mean correlation
    coefficient resulting from 100 repetitions of the k-fold cross validation.
    The blue smoothing line was fitted using a locally weighted polynomial
    regression and serves to aid the eye in detecting the trends. Correlation
    coefficients suggest that our prediction was significant and robust,
    evidenced by the fact that the confidence intervals of \(\bar{r}_{s,
    realized}\) and \(\bar{r}_{s, random}\) did overlap and by the fact that
    there was strong and significant correlation between ranks and associated
    frequency for realized steps.}
    \label{PermeabilityResults}
  \end{center}
\end{figure}

@@

\begin{figure}[hbtp]
  \begin{center}
    \begin{tikzpicture}
        \node[anchor=south west,inner sep=0] (image) at (0,0,0) {
          \begin{minipage}{0.65\textwidth}
            \includegraphics[width = \textwidth]{99_PermeabilityMap.pdf}
          \end{minipage}
        };
        \begin{scope}[x={(image.south east)},y={(image.north west)}]
           %  % next four lines will help you to locate the point needed by
           %  % forming a grid. comment these four lines in the final picture.↓
           % \draw[help lines,xstep=.1,ystep=.1] (0,0) grid (1,1);
           % \draw[help lines,xstep=.05,ystep=.05] (0,0) grid (1,1);
           % \foreach \x in {0,1,...,9} { \node [anchor=north] at (\x/10,0) {0.\x}; }
           % \foreach \y in {0,1,...,9} { \node [anchor=east] at (0,\y/10) {0.\y};}
           %  % upto here
          % \node[text=white, circle, scale=1, font=\bfseries, inner sep = 0.5pt
          %   , draw=white] (No1) at (0.440, 0.350){1};
          % \node[text=white, circle, scale=1, font=\bfseries, inner sep = 0.5pt
          %   , draw=white] (No2) at (0.520, 0.438){2};
        \end{scope}
    \end{tikzpicture}
    \caption{Predicted permeability surface for the extent of the KAZA-TFCA.
    Permability was predicted by calculating selection scores \(w(x) =
    exp(\beta_1 x_1 + \beta_2 x_2 + ... + \beta_n x_n)\) for each pixel based on
    the pixel's underlying covariates (\(x_i\)) and estimated habitat
    preferences (\(\beta_i\)). Areas that dispersers find easy to traverse are
    depicted in bright colors. Bold white lines delineate the borders of the
    KAZA-TFCA, whereas dashed white lines show country borders.}
    \label{PermeabilityMap}
  \end{center}
\end{figure}

\begin{table}[h]
  \caption{Comparison of median permeability (interquantile range in brackets)
  across countries, separated according to areas within and outside the
  KAZA-TFCA, as well as within and outside formally protected areas. High values
  indicate high permeability, whereas low values correspond to low
  permeability.}
  \label{PermeabilityComp}
  \centering
  \begin{tabular}{llllll}
    \toprule
    \multicolumn{1}{c}{ } & \multicolumn{2}{c}{KAZA-TFCA} & \multicolumn{2}{c}{Protection Status} & \multicolumn{1}{c}{ } \\
    \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
    Country & Inside & Outside & Protected & Pastoral & Overall\\
    \midrule
    Angola & 0.41 (0.42) & 0.18 (0.35) & 0.41 (0.42) & 0.19 (0.35) & 0.26 (0.40)\\
    Botswana & 0.27 (0.30) & 0.15 (0.17) & 0.29 (0.35) & 0.16 (0.19) & 0.20 (0.26)\\
    Namibia & 0.23 (0.30) & 0.13 (0.18) & 0.24 (0.30) & 0.11 (0.15) & 0.16 (0.24)\\
    Zambia & 0.08 (0.11) & 0.04 (0.06) & 0.07 (0.12) & 0.04 (0.06) & 0.05 (0.08)\\
    Zimbabwe & 0.08 (0.20) & 0.06 (0.05) & 0.10 (0.21) & 0.06 (0.04) & 0.06 (0.08)\\
    \hline
    Overall & 0.19 (0.32) & 0.08 (0.16) & 0.18 (0.32) & 0.08 (0.17) & 0.11 (0.23)\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\newpage
\appendix
\section{Appendix}
\subsection{Net Squared Displacement}
\label{Appendix:GPSData}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = 0.8\textwidth]{99_NSD.pdf}
    \caption{NSD displacement graph for one of our dispersers. Blue colors
    indicate the period during which we calssified the individual as
    dispersing.}
    \label{NSD}
  \end{center}
\end{figure}

\newpage
\subsection{GPS Data}
\label{Appendix:GPSData}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width = 0.9\textwidth]{99_Trajectories.pdf}
    \caption{Illustration of the dispersal trajectories that we recorded. Each
    color represents a different dispersing coalition. All coalitions departed
    from the core study area, which is indicated by the white rectangle. The
    coalition dispersing towards the far east of the map covered over 360 km in
    under 10 days.}
    \label{Trajectories}
  \end{center}
\end{figure}
